**Evaluation of machine learning methods for 16S rRNA gene data**

### 2019-06-07 submission/manuscript.Rmd
redo interpret figures based on Jenna

**Permutation importance workflow.**

>>>>

**Permutation importance workflow.**
We created a Spearman's rank-order correlation matrix, corrected for multiple pairwise comparisons. We then defined correlated OTUs as having perfect correlation (correlation coef=1 and p<0.01).Other OTUs were permuted individually to get permutation importance but the correlated ones are grouped together and permuted at the same time. The reported OTUs that have impact on testing AUROC are reported in Figures xxx. If we want we can decrease the correlation coefficient to consider OTUs that are correlated with ecological consequences but this was out of the scope of this study but will be followed up in further analyses.
